---
title: "Case Study 8 Karis Saplys"
author: "Karis Saplys"
date: "2022-10-31"
output: 
  html_document:
    theme: cosmo
    keep_md: TRUE
    code_folding: 'hide'
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(knitr)
library(lubridate)
library(readr)
library(haven)
library(downloader)
library(foreign)
library(readxl)
library(corrplot)
library(stringr)

```

```{r}
temp1 <- tempfile()
download("https://github.com/WJC-Data-Science/DTS350/raw/master/sales.csv", temp1, mode = "wb")
sales <- read_csv(temp1)
```

```{r}
head(sales)
tail(sales)
str(sales)
```

```{r}
sales <- with_tz(sales, tzone = "US/Mountain")
head(sales)
```

```{r}
sales_by_hour <- sales %>%
  mutate(hourly = ceiling_date(Time, "hour")) %>%
  mutate(daily = ceiling_date(Time, "day")) %>%
  mutate(Hour = hour(hourly)) %>%
  group_by(Name, Hour) 

head(sales_by_hour)
```

```{r}
hours_of_operation <- ggplot(sales_by_hour, aes(x=Hour, y=Amount )) +
  geom_bar(stat="identity") +
  theme() +
  labs(x="Time of Sales (24-Hour Clock)", y="Amount of Sales", title="Amount of Sales by Hour of Operation")

hours_of_operation
```
Based on the data and this associated visualization, it would seem that the most prudent hours of operation would be between 10am and no later than 10pm, in order to capture the highest volume of sales.

```{r}
by_day <- sales %>%
  mutate(daily = ceiling_date(Time, "day")) %>%
  mutate(Daily = wday(daily)) %>%
  group_by(Name, Daily)

tail(by_day)
```

```{r}
daily_traffic <- ggplot(by_day, aes(x=Daily, y=Amount )) +
  geom_bar(stat="identity") +
  theme() +
  labs(x="Day of the Week (1 = Sunday)", y="Amount of Sales Traffic", title="Sales Traffic by Day of the Week")

daily_traffic
```
Friday and Saturday seem to have the largest volumes of sales traffic, with significant drop offs on Sunday and Monday, likely related to the nature of the businesses. Based on the data, I'd recommend being fully staffed an operational Tuesday through Saturday. 

```{r}
tot_sales<- sales%>%
  group_by(Name)%>%
  summarise(across(Amount, sum))

tot_sales
```

```{r}
final_viz <- ggplot(tot_sales, aes(x=Name, y=Amount )) +
  geom_bar(stat="identity" ) +
  theme()+
  labs(x="Company Names", y="Total Amount of Sales", title="Total Sales by Company")

final_viz
```
Based on the aggregate amount of total sales, it would appear that HotDiggity is the best company to invest in due to genrating the most revenue. Once invested, I recommend hours of operation of 10am-10pm, with company locations being open Tuesday through Saturday. 
