---
title: "Task 7 Karis Saplys"
author: "Karis Saplys"
date: "2022-09-19"
output: 
  html_document:
    theme: cosmo
    keep_md: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r loading packages}
library(lubridate)
library(readr)
library(tidyverse)
library(knitr)
library(downloader)
library(dplyr)
```

```{r loading in data}
download.file("https://raw.githubusercontent.com/hadley/r4ds/master/data/heights.csv", "heights")

Heights <- read_csv("heights")
head(Heights)
str(Heights)
```

```{r new data set}
HeightEd <- Heights %>%
  mutate(ed = as.factor(ed)) %>%
  mutate(ed = fct_recode(ed,
                         "primary" = "3",
                         "primary" = "4",
                         "primary" = "5",
                         "primary" = "6",
                         "secondary" = "7",
                         "secondary" = "8",
                         "secondary" = "9",
                         "secondary" = "10",
                         "secondary" = "11",
                         "highschoolgrad" = "12",
                         "associates" = "13",
                         "associates" = "14",
                         "associates" = "15",
                         "bachelors" =  "16",
                         "mastersdoctorate" = "17",
                         "mastersdoctorate" = "18"))
HeightEd
```

```{r race and education}
race_ed <- HeightEd %>%
  group_by(race) %>%
  count(ed)

race_ed

ggplot(data=race_ed, mapping=aes(ed, n, fill=race)) +
  geom_bar(stat="identity", position="stack") 
```

```{r sex and education}
sex_ed <- HeightEd %>%
  group_by(sex) %>%
  count(ed)

sex_ed

ggplot(data=sex_ed, mapping=aes(ed, n, fill=sex)) +
  geom_bar(stat="identity", position="dodge") 
```

```{r race and earnings}
race_earn <- HeightEd %>%
  group_by(race) %>%
  summarise(Avg = mean(earn))

race_earn

ggplot(data=race_earn, mapping=aes(race, Avg, fill=race)) +
  geom_bar(stat="identity", position="dodge") +
  labs(y = "Mean Earnings",
       x = "Race",
       title = "Average Earnings By Race") +
  theme(legend.position = "none")
```

By undergoing this process, I learned how to expertly layer and structure items within ggplot. Moreover, I learned how to alter and manipulate datasets to draw out specific information using dplyr commands (mutate, summarise, etc.). Finally, I became more and more acquaintdd with the mechanics and inner workings of r, such as manipulating datatypes to becomes factors for ease of creating visualizations. 
