---
title: "Case Study 7 Karis Saplys"
author: "Karis Saplys"
date: "2022-10-11"
output: 
  html_document:
    theme: cosmo
    keep_md: TRUE
    code_folding: 'hide'
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(readr)
library(haven)
library(downloader)
library(foreign)
library(readxl)
```

Code chunks are unnamed to allow clean processing of visualizations into github.
```{r}
germanconscript <- read_dta(url("https://github.com/WJC-Data-Science/DTS350/blob/master/germanconscr.dta?raw=true"))

germanprison <- read_dta(url("https://github.com/WJC-Data-Science/DTS350/blob/master/germanprison.dta?raw=true"))

heights <- read_csv(url("https://raw.githubusercontent.com/hadley/r4ds/master/data/heights.csv"))

heights2 <- tempfile()
download("https://github.com/WJC-Data-Science/DTS350/blob/master/Height.xlsx?raw=true", heights2, mode = "wb")
heights1 <- read_xlsx(heights2, skip = 2)

heights_se <- tempfile()
download("https://github.com/WJC-Data-Science/DTS350/raw/master/Heights_south-east/B6090.DBF?raw=true", heights_se, mode = "wb")
se_heights <- read.dbf(heights_se)
```

```{r}
wisconsin <- tempfile()
download("http://www.ssc.wisc.edu/nsfh/wave3/NSFH3%20Apr%202005%20release/main05022005.sav", wisconsin, mode = "wb")
WisconsinData <- read_sav(wisconsin)
```

```{r}
str(WisconsinData)
```

```{r}
heights_tidy <- heights1 %>%
  pivot_longer(3:203, names_to = "years", values_to = "heights.cm", values_drop_na = TRUE) %>%
  mutate(year_decade = years, height.in = heights.cm / 2.54) %>%
  separate(years, into = c("century", "decade"), sep = -2) %>%
  separate(decade, into = c("decade", "year"), sep = -1)

write.csv(heights_tidy, "heights_tidy.csv", row.names = TRUE)
```

```{r}
German_Conscript <- germanconscript %>%
  mutate(birth_year = bdec,
         height.cm = height,
         height.in = height.cm / 2.54,
         study_id = 'germanconscript') %>%
  select(birth_year, height.cm, height.in, study_id)

German_Prison <- germanprison %>%
  mutate(birth_year = bdec,
         height.cm = height,
         height.in = height.cm / 2.54,
         study_id = 'germanprison') %>%
  select(birth_year, height.cm, height.in, study_id)

heights_data <- heights %>%
  mutate(birth_year = 1950,
         height.cm = height * 2.54,
         height.in = height,
         study_id = 'heights') %>%
  select(birth_year, height.cm, height.in, study_id)

SouthEast_heights_data <- se_heights %>%
  mutate(birth_year = SJ,
         height.cm = CMETER,
         height.in = CMETER / 2.54,
         study_id = 'se_heights') %>%
  select(birth_year, height.cm, height.in, study_id)

Wisconsin_Tidy <- WisconsinData %>%
  mutate(birth_year = as.numeric(DOBY) + 1900,
         height.cm = RT216I * 2.54,
         height.in = RT216I,
         study_id = 'WisconsinData') %>%
  select(birth_year, height.cm, height.in, study_id)
```

```{r}
head(WisconsinData)
```

```{r}
combine <- bind_rows(German_Conscript,German_Prison,heights_data,SouthEast_heights_data,Wisconsin_Tidy)

write.csv(combine, "Combined.csv", row.names = TRUE)
```

```{r}
germany_filter <- heights_tidy %>%
  filter(`Continent, Region, Country` == 'Germany')
```

```{r}
ggplot(data = heights_tidy, aes(x = year_decade, y = height.in)) +
  geom_boxplot(alpha = 0.5) +
  geom_point(data = germany_filter, color = "red") +
  theme_bw() +
  labs(x = "Decade",
       y = "Height in.",
       title = "Male Heights in Germany Over Time")
```

It is easy to see that average height is undoubtedly increasio=ng over time, as evidenced by a clear trend among the same exact sampled demographic each decade (males in Germany). The hypothesis of The Scientific American that argues that humans have been getting taller over the years seems both logical and correct.

```{r}
ggplot(combine, aes(x = birth_year, y = height.in)) +
  geom_col() +
  facet_wrap(~ study_id, scales = 'free') +
  theme_bw() +
  labs(x = "Birth Year",
       y = "Height Quantities",
       title="Combined Data")
```

