---
title: "Case Study 5 Karis Saplys"
author: "Karis Saplys"
date: "2022-09-27"
output: 
  html_document:
    theme: cosmo
    keep_md: TRUE
    code_folding: 'hide'
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(downloader)
library(readxl)
```

A brief summary of the article: The FiveThirtyEight article discusses the methodology and structure of the site's datatset of firearm related deaths and their specific causes. The article discusses where the information was sourced, how it determined where ambiguous events fit into their categories, how it segmented information by race, gender, age, etc. and overall how the information wascompiled for public viewing and use in research. All in all, the article seeks to provide the information and an outline for finding data-driven solutions to the problem of firearm-related deaths in the United States.

```{r reading in the data}
GunData <- tempfile()
download("https://raw.githubusercontent.com/fivethirtyeight/guns-data/master/full_data.csv", GunData, mode = "wb")
gunData <- read_csv(GunData)
gunData_new <- gunData %>%
  filter(age != "", intent != "")
str(gunData)
head(gunData)
```

```{r altering the dataset}
gunsData <- gunData_new %>%
  mutate(agegroup =
          case_when(
            age >= 0 & age <= 14 ~ "under 15",
            age >= 15 & age <= 34 ~ "15-34",
            age >= 35 & age <= 64 ~ "35-64",
            age >= 65 ~ "65+"),
         agegroup = fct_relevel(agegroup, 
            "under 15", "15-34", "35-64", 
            "65+"))
```

```{r plot 1}
ggplot(data = gunsData, aes(x = agegroup, fill = sex)) +
  geom_bar() +
  facet_wrap(~intent, nrow = 2, scales = 'free') +
  scale_fill_manual(values = c('#FD6D6D', '#5A84D3')) +
  ggtitle("Gun deaths by cause for different age groups") +
  theme_bw()
```

```{r plot 2}
ggplot(data = gunData_new, aes(x = age, fill = intent)) +
  geom_density(position = 'fill', alpha = .6) +
  facet_wrap(~sex) +
  scale_fill_manual(values = c("#8CDBAA","#FFA727","lightslateblue","hotpink")) +
  ggtitle("Proportions of Gun Death Causes for Males and Females") +
  theme_bw()
```

```{r additional plot 1}
season <- gunData_new %>%
  filter(education != "") %>%
  mutate(seasons = as.factor(fct_collapse(month,
          "Spring" = c("03", "04", "05"),
          "Summer" = c("06", "07", "08"),
          "Fall" = c("09", "10", "11"),
          "Winter" = c("12", "01", "02"))),
         seasons = fct_relevel(seasons, 
            "Spring", "Summer", "Fall", 
            "Winter")
  )

head(season)

ggplot(season, aes(intent, fill = education)) +
  geom_bar() +
  facet_wrap(~seasons, scales = "free") +
  ggtitle("Number Of Gun Deaths By Cause and Education Level In Each Season") +
  theme_bw()
```
In this plot, the number of gun deaths by intent are plotted for each season in a bar chart. The bar charts' bars are broken into sections by victims' level of education.

```{r additional plot 2}
ggplot(season, aes(seasons, fill = race)) +
  geom_bar() +
  facet_wrap(~race, scales = 'free') +
  ggtitle("Number of Gun Deaths Per Season By Race") +
  theme_bw() +
  theme(legend.position = 'none')
```
In this plot, the number of gun deaths per season by victims' race are plotted in a bar chart. The bar charts are faceted so that each chart represents the seasonal statistic data of a different race.
