---
title: "Task 2 DTS 350 Saplys"
author: "Karis Saplys"
date: "2022-08-31"
output: 
  html_document:
    theme: cosmo
    keep_md: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r loading Knitr package}
library(knitr)
```

```{r computation}
sin(pi/4)
```

using R as a calculator here in this case

```{r assignment operator}
x <- 10/3

```


```{r sequence}
MySequence <- seq(1,50, length.out = 7)
MySequence
```

sequence runs from 1 to 50, and contains 7 equally spaced out numbers

```{r vector}
my_vector <- c(1, 5, 12, 31, 19)
```

vector created using the compile/concatonate function

```{r determining result}
7+5==12
```

== asks whether the preceding statement is TRUE or FALSE

```{r or statement}
(7+4=12)|(5-4=1)
```

The "or" operator here combines the two statements. However, the equals sign in r functions as an assignment operator, while == is used to evaluate the true/false nature of an expression.

##Chapter 4 Excercises 1-3

#1
my_variable <- 10
my_varıable
#> Error in eval(expr, envir, enclos): object 'my_varıable' not found

This code doesnt work because when the variable "my_variable" is called, the "i" is replaced with a different character, meaning the typed variable doesn't exist.

#2
```{r incorrect code question 2}
#library(tidyverse)

#ggplot(dota = mpg) + 
  #geom_point(mapping = aes(x = displ, y = hwy))

#fliter(mpg, cyl = 8)
#filter(diamond, carat > 3)
```
##Corrected Code Below

library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl == 8)
filter(diamonds, carat > 3)

Code has been fixed so that it runs accordingly. Errors consisted of typos (dota instead of data, fliter instead of filter), use of = instead of ==, and diamond (which doesn't include thevariable carat) instead of diamonds.

#3
Keyboard shortcut reference pulls up. Can also be found in tools-keyboard shortcuts help.