---
title: "Task 20 Karis Saplys"
author: "Karis Saplys"
date: "2022-11-18"
output: 
  html_document:
    theme: cosmo
    keep_md: TRUE
    code_folding: 'hide'
editor_options: 
  chunk_output_type: console
---

#RECREATING CASE STUDY 4 WITH ANIMATIONS ON 'DELTA DELAYS BY NYC ORIGIN AIRPORT' GRAPH 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r loading packages}
library(lubridate)
library(readr)
library(tidyverse)
library(knitr)
library(downloader)
library(dplyr)

library(ggplot2)
library(gganimate)
library(gifski)
```

```{r loading in the data}
library(nycflights13)
?flights
head(flights)
str(flights)
```

2. Which origin airport is best to minimize my chances of a late arrival when I am using Delta Airlines?

From my findings, I can tell you that Newark (EWR) had the fewest delayed Delta Airlines flights. On the other hand, LGA had the most Delta fliughts that were delayed. As such, when using Delta Airlines, I would say that EWR is the best airport to use if you are looking to avoid any kind of late arrival.

```{r DeltaDelaysAnimViz}
freq_delay <- flights %>%
  filter(carrier == "DL", arr_delay > 0) %>%
  group_by(origin) %>%
  count()
freq_delay

delta_delay_plot <- ggplot(data=freq_delay, mapping=aes(origin, n, fill=origin)) +
  geom_bar(stat="identity", position="dodge") +
  labs(y = "Number of Delays",
       x = "Airport of Origin",
       title = "Number of Delayed Delta Airlines FLights Per Airport") +
  theme(legend.position = "none")

delta_delay_plot + transition_states(n,
    transition_length = 2,
    state_length = 1
  ) +
  enter_fade() +
  exit_shrink() +
  ease_aes('sine-in-out')

anim_save("DeltaDelaysAnimViz.gif")
```
