---
title: "Task 5 Karis Saplys"
author: "Karis Saplys"
date: "2022-09-05"
output: 
  html_document:
    theme: cosmo
    keep_md: true
editor_options: 
  chunk_output_type: console
code_folding: 'hide'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r installing various packages}
library(readr)
library(tidyverse)
library(knitr)
library(downloader)
library(dplyr)
```

```{r importing data 1}
SoloData <- read_csv("solo-artist-followers.csv")
SoloData
str(SoloData)
```

Data imported correctly as characters.

```{r importing data 2}
BillboardData <- read_csv("billboard-hits.csv")
BillboardData
str("BillboardData")
```

Data imported correctly as characters.

```{r removing singers without 6 top 100 hits}
sixtop100hits <- BillboardData %>%
  group_by(name) %>%
  filter(n() > 6, band != "")
sixtop100hits
```

Singers without 6 top 100 hits removed.

```{r finding bands}

sixtop100_bands <- BillboardData %>%
  group_by(name) %>%
  filter(name %in% sixtop100hits$band)
sixtop100_bands
```

Corresponding data in the data set for the top singers’ bands.

```{r}
ggplot(data = sixtop100hits, mapping=aes(x = peak_date, y = peak_rank, color = name, group = name)) +
  geom_point() +
  geom_line() +
  geom_point(data = sixtop100_bands, color = "black") +
  geom_line(data = sixtop100_bands, color = "black", linetype = "dotted") +
  facet_wrap(~ band, scales = "free") +
  xlab("peak_date") + ylab("peak_rank") +
  theme_bw()
```

From the above plots, I can observe that in general, most bands experienced peak popularity between 2014 and 2019, with a few exceptions. Destiny's CHild seems to be among the most consistent, with periodic spikes likely corresponding to new releases of music. 

```{r source 1}
climate_data <- read_csv("Climate Data.csv")
head(climate_data)
str(climate_data)
```
https://www.kaggle.com/datasets/csafrit2/latest-global-temperatures 

The above dataset contains NOAA satelite data measuring natural microwave thermal emissions from various layers of the atmosphere. The data comes from 15 different instruments, and is updated every year to show changes in atmospheric temperatures. 

```{r source 2}
rent_index1 <- read_csv("price.csv")
rent_index2 <- read_csv("pricepersqft.csv")
head(rent_index1)
head(rent_index2)
str(rent_index1)
str(rent_index2)
```
https://www.kaggle.com/datasets/zillow/rent-index

Zillow's sector-leading economics team compiles various real estate, rental and mortgage-related metrics data to answer important questions about the state of the US housing market. Data are compiled from 500 different markets nationwide. It is important to note that the data are broken up into 2 different sets (price and pricepersqft).

```{r source 3}
election_2020 <- read_csv("president_county.csv")
head(election_2020)
str(election_2020)
```
https://www.kaggle.com/datasets/unanimad/us-election-2020

The above dataset conatins county-level data from the 2020 US presidential election. 
